# Clustering with R by Francis Gikaru Njeri

# Kira Plastinina (Links to an external site.) is a Russian brand that is sold through a # defunct chain of retail stores in Russia, Ukraine, Kazakhstan, Belarus, China, #Philippines, and Armenia. The brand’s Sales and Marketing team would like to understand # their customer’s behavior from data that they have collected over the past year. More # specifically, they would like to learn the characteristics of customer groups.

# Perform clustering stating insights drawn from your analysis and visualizations.
# Upon implementation, provide comparisons between the approaches learned this week i.e. # K-Means clustering vs Hierarchical clustering highlighting the strengths and #limitations of each approach in the context of your analysis. 
# Your findings should help inform the team in formulating the marketing and sales #strategies of the brand. 
```{r}
install.packages("caret")
install.packages("corrplot")
install.packages("clustvarsel")
install.packages("mclust")
install.packages("wskm")
install.packages("cluster")
install.packages("FSelector")
```


```{r}
# calling libraries
library(ggplot2)
library(mclust)
library(caret)
library(corrplot)
library(clustvarsel)
library(wskm)
library(cluster)
library(FSelector)
```

```{r}
# loading the data source
df <-read.csv('/home/francis/Documents/R files/ads classification with R/online_shoppers_intention.csv')

# previewing the dataset
head(df)
```
```{r}
# data cleaning
# checking for null values
colSums(is.na(df))
```


```{r}
# dealing with the null values
na.omit(df)
```
```{r}
# summary of the numeric columns
summary(df)
```
```{r}

```

Check the Data
Perform Data Cleaning
Perform Exploratory Data Analysis  (Univariate, Bivariate & Multivariate)
Implement the Solution
Challenge the Solution
Follow up Questions
